---
title: "Spatial Project"
author: "Chansoo Song"
date: "10/2/2018"
output: pdf_document
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo=TRUE,tidy=TRUE)
  library(ggplot2)
  library(dplyr)
  # devtools::install_github("dkahle/ggmap", ref = "tidyup")
  library(ggmap) # install using line above
```

## Load Data

```{r}
# Stop and Frisk Data
load('Data/stops2013clean.RData')

# CSV containing precincts and corresponding borough
prec_bor = read.csv('Data/prec_to_boroughs.csv', header = F, stringsAsFactors = F)
```

## Clean Data

```{r}
# Column names of prec_bor
colnames(prec_bor) = c('precinct','borough')

# Subset stop and frisk data
cols_to_keep = c("id",
                 "lon",
                 "lat",
                 "year",
                 "precinct",
                 "found.contraband",
                 "found.pistol",
                 "found.rifle",
                 "found.assault",
                 "found.knife",
                 "found.machinegun",
                 "found.other",
                 "found.gun",
                 "found.weapon")
df = stops2013clean[,cols_to_keep]

# Create "Hits" column in Stop and Frisk Data
cols_hit = c("found.contraband",
                 "found.pistol",
                 "found.rifle",
                 "found.assault",
                 "found.knife",
                 "found.machinegun",
                 "found.other",
                 "found.gun",
                 "found.weapon")
# hits column
df$hit = ifelse( apply(df[,cols_hit],1,sum)>0, 1, 0)

# Merge Stop and Frisk Data and Precinct_Borough Data
df$precinct = as.integer(as.character(df$precinct))
df = df %>% 
  left_join(prec_bor, by = 'precinct')

# Don't need these anymore. 
rm(stops2013clean)
rm(prec_bor)
```

## Set Radius then Pick center with largest number of stops within radius

The "parallel_dist_spacial.R" and "parallel_dist_spatial_bk.R" were run on NYU's HPC Clusters to identify the centers of circles containing the most stops. We tried different radii: 0.01, 0.0075, and 0.005.

These centers were identified for each borough then saved with corresponding coordinates into the "results" folder. Here, I compared the top candidate centers from each borough to identify a single center with the most stops within the radius.

```{r}
# Radius
radius = 0.01

boroughs = c("Bronx", "Brooklyn", "Manhattan", "Queens", "Staten Island")
result_files = paste('results/',boroughs,'_',radius,'_result.csv',sep='')

candidate_centers = as.data.frame(matrix(0,nrow=5,ncol=4))
colnames(candidate_centers) = c('X','lon','lat','n')

for (i in 1:length(result_files)) {
  result_file = read.csv(result_files[i], header=T)
  candidate = result_file[1,c('X','lon','lat')]
  # Distances between Center and All Stops
  dists = sqrt((df$lon - candidate$lon)^ 2 + (df$lat - candidate$lat)^ 2)
  # Count Stops in Circle
  n = sum(ifelse(dists < radius, 1, 0))
  
  candidate_centers[i,] = c(candidate, n)
}


```


## Hit Rate within Circle

```{r}
center = candidate_centers %>%
  arrange(-n) %>%
  dplyr::select(X,lon,lat) %>%
  head(1)
            
# Distances between Center and All Stops
dists = sqrt((df$lon - center$lon)^ 2 + (df$lat - center$lat)^ 2)
  
# Hit Rate of Stops within Radius
in_circle = ifelse(dists < radius, 1, 0)
center_hit_rate = sum(in_circle * df$hit) / sum(in_circle)

# Store number of stops in this circle for later
n_in_circle = sum(in_circle)
```

## Test for Significance of Hit Rate in the High Stop Circle using Fixed Radius

```{r}
# Random sample of centers
n_samples = 1000
samples_idx = sample(nrow(df), n_samples)
centers = df[samples_idx,c("id","lon","lat","hit")]

# Get Hit Rates for Circles of Fixed Radius around this random sample of centers
hit_rates_radius = rep(NA, n_samples)
for(i in 1:n_samples){
  # Longitude and Latitude of Center
  center_lon = centers[i,c("lon")]
  center_lat = centers[i,c("lat")]
  
  # Distances between Center and All Stops
  dists = sqrt((df$lon - center_lon)^ 2 + (df$lat - center_lat)^ 2)
  
  # Hit Rate of Stops within Radius
  in_circle = ifelse(dists < radius, 1, 0)
  
  hit_rates_radius[i] = sum(in_circle * df$hit) / sum(in_circle)
}

plot(density(hit_rates_radius), main = 'Sampling Distribution of Hit Rates')
abline(v = center_hit_rate, col = 3)
```

## Test for Significance of Hit Rate in the High Stop Circle using Random Circles containing same number of Stops

```{r}
# Random sample of centers
n_samples = 1000
samples_idx = sample(nrow(df), n_samples)
centers = df[samples_idx,c("id","lon","lat","hit")]

# Get Hit Rates for Circles of Fixed Radius around this random sample of centers
hit_rates_n = rep(NA, n_samples)
for(i in 1:n_samples){
  # Longitude and Latitude of Center
  center_lon = centers[i,c("lon")]
  center_lat = centers[i,c("lat")]
  
  # Distances between Center and All Stops
  dists = sqrt((df$lon - center_lon)^ 2 + (df$lat - center_lat)^ 2)
  
  # Hit Rate of N number of nearest Stops to Center
  n_short_dists = sort(dists, decreasing = F)[1:n_in_circle]
  idx_short_dists = which(dists %in% n_short_dists)
  
  hit_rates_n[i] = sum(df$hit[idx_short_dists]) / n_in_circle
}

plot(density(hit_rates_n), main = 'Sampling Distribution of Hit Rates')
abline(v = center_hit_rate, col = 3)
```


## Test for Significance of Spillover Effect on Stops near main circle but just outside

```{r}
# Random sample of centers
n_in_circle

# Distances between Center and All Stops
dists = sqrt((df$lon - center$lon)^ 2 + (df$lat - center$lat)^ 2)
  
# Hit Rate of Stops within Radius
extension.tries = matrix(ncol=2,nrow=20)

x = seq(0.01,0.0125,length=20)
for(i in 1:20){
  in_circle = ifelse(dists > radius & dists < radius + x[i], 1, 0)
  extension.tries[i,] = c(x[i],sum(in_circle)-n_in_circle)
}
extension.tries

# Extend radius by 0.01210526
in_circle = ifelse(dists > radius & dists < radius + 0.01210526, 1, 0)
spillover_hit_rate = sum(in_circle * df$hit) / sum(in_circle)

plot(density(hit_rates_radius), main = 'Sampling Distribution of Hit Rates')
abline(v = center_hit_rate, col = 3)
abline(v = spillover_hit_rate, col = 2)
```








###########################################################################
##### IGNORE BELOW FOR NOW
###########################################################################

## Draw Circles

```{r}
make_circles <- function(centers, radius, nPoints = 100){
    circleDF <- data.frame(ID = rep(centers$X, each = nPoints))
    angle <- seq(0,2*pi,length.out = nPoints)
    circleDF$lon = unlist(lapply(centers$lon, function(x) x + radius * cos(angle)))
    circleDF$lat = unlist(lapply(centers$lat, function(x) x + radius * sin(angle)))
    return(circleDF)
}


# here is the data frame for all circles
myCircles <- make_circles(center, 0.01)
```

## Plot on Map

```{r}
# colnames(centers) = c('X','lon','lat','hit')
myCircles <- make_circles(centers[1:30,], 0.01)

register_google(key = "AIzaSyC4ABT6F3JznHUr-uCTAFs4R3lgDYNul_k")
nyc_map = get_map(location = c(lon = -73.94316, lat = 40.6965), 
                  zoom = 11, 
                  maptype = "satellite",
                  source = "google")
nycMap = ggmap(nyc_map, extent = "panel", legend = "bottomright")
nycMap

#  5% Sample
df.sampled = df[sample(nrow(df),nrow(df)*.05),]
stops = geom_point(aes(x=lon, y = lat), 
                   data = df.sampled, 
                   color = df.sampled$hit+1,
                   alpha = 0.2)

nycMap + stops +
    geom_polygon(data = myCircles, aes(lon, lat), color = "red", alpha = 0) 

```












